\section{Parallel execution and shared user-subroutine state}
\label{sec:externaldb-parallelization}

The use of \texttt{UEXTERNALDB} is not, by itself, incompatible with parallel
Abaqus/Standard execution.  The callback provides analysis- and
increment-boundary points at which external data can be initialized or
exchanged.  The relevant correctness question is instead how that information
is stored and subsequently accessed by element and material subroutines.

The present implementation transfers phase and history information through
mutable Fortran \texttt{COMMON} blocks and also contains \texttt{SAVE} and
\texttt{DATA} storage.  Threads in one process share these objects, so
concurrent UEL and UMAT calls can create read--write or write--write races
unless ownership is guaranteed or access is synchronized.  Separate MPI
processes present a different problem: each rank has its own common-block
instance, and common storage therefore cannot provide inter-rank exchange.
Distributed support would require an explicit ownership and communication
design at defined synchronization points.

The earlier D2C comparison produced identical serial and one-rank/four-thread
phase, history, reaction-force, energy, and increment results.  This is
positive but case-specific evidence; it does not prove general thread safety.
Stage~P therefore isolates the question in an eight-physical-element model.
Bounded diagnostics record callback identity, rank and thread identifiers,
first access to each shared location, initialization, live writer conflicts,
and final call counts.  A serial diagnostic is the mandatory reference before
one four-thread characterization.  MPI, hybrid, and production claims remain
withheld.

The first instrumented serial package terminated before element execution
because \texttt{GETRANK} was called during \texttt{UEXTERNALDB} initialization.
The subsequent uninstrumented P3-SB model compiled, linked, completed
Abaqus/Standard, and produced complete eight-element/four-integration-point
state evidence. Its automated lane nevertheless retained a technical
validation-failure classification because the required standard-output and
status files were copied only after validation. An isolated replay of the
unchanged validator against the finalized evidence passed every frozen serial
gate, including 32/32 state records, finite reaction-force and energy
histories, monotone phase/history fields, and 13 increment/attempt records.
This supports the eight-element serial baseline but no thread- or MPI-safety
claim. The subsequent P3-SM0 test used only constant \texttt{UEXTERNALDB},
UEL, and UMAT markers; rank/thread and mutex utilities remained excluded.
The one authorized serial job completed with scheduler and solver exit zero,
all four markers observed, no signal 11, complete 32/32 state coverage, and
zero phase, history, or transfer violations. Thus, the accepted serial model
completes with this minimal callback plumbing. The result does not establish
\texttt{GETRANK} or \texttt{GETTHREADID} safety, shared
\texttt{COMMON}/\texttt{SAVE} thread safety, four-thread repeatability, MPI,
or hybrid support.
