\chapter{Interrupted-Transfer Checkpoint Correction}
\label{chap:d3d-a1-checkpoint}

\section{Methodology}

The transferred checkpoint was assessed at
\(U_2=0.003000000026077032\,\mathrm{mm}\).  The recovered F3 phase field at
6,601 nodes was retained as the irreversibility lower bound, while the 25,600
actual F3 integration-point history values were held fixed.  No mesh,
material, phase-field formulation, Fortran implementation, solver tolerance,
or loading parameter was changed.

The corrected phase field was obtained offline with a deterministic
primal--dual active-set iteration.  At each iteration, active nodes were fixed
at the recovered F3 lower bound and the reduced phase system was solved for the
free nodes.  Nodes violating the lower bound were reactivated, while active
nodes with a multiplier below \(-10^{-8}\) were released.  Acceptance required
a free residual infinity norm no greater than \(10^{-8}\), a minimum active
multiplier no smaller than \(-10^{-8}\), an active-bound error no greater than
\(10^{-10}\), complete phase/history coverage, no non-positive Jacobian
determinants, and no increase of the phase functional.

\section{Offline Correction Result}

The offline correction converged deterministically in seven iterations to
6,374 active and 227 free nodes.  The final free residual infinity norm was
\(2.1176\times10^{-21}\), the minimum active multiplier was
\(-9.99696\times10^{-9}\), and the active-bound error was zero.  The phase
functional changed by \(-1.6759\times10^{-10}\).  No phase-decrease,
history-change, lower-bound, state-reset, or non-positive-Jacobian violation
was detected.

These results establish that the corrected phase field is mathematically
admissible for the frozen F3 history under the prescribed KKT gates.  The
result classification is
\texttt{stage\_d3d\_a1\_checkpoint\_obstacle\_update\_pass}.  The associated
package contains the corrected phase, unchanged actual F3 history, original F3
lower bound, and converged 6,374/227 membership.

\section{Mechanical-Checkpoint Qualification}

The candidate package is not an accepted Abaqus restart state.  Mechanical
re-equilibration was intentionally placed behind a fixed-phase datacheck and
checkpoint-hold gate.  Three bounded datacheck attempts terminated before
Abaqus execution:

\begin{enumerate}
  \item job \texttt{1378003.mmaster02} compared a Windows-derived Fortran
        checksum with the LF-normalized Linux checkout;
  \item job \texttt{1378004.mmaster02} used Python assignment-expression
        syntax unsupported by the compute-node default Python~3.6; and
  \item job \texttt{1378005.mmaster02} reached a common preflight in which
        \texttt{git} was unavailable after the module purge/load sequence.
\end{enumerate}

None of these jobs compiled the user subroutine, processed the Abaqus input, or
completed a datacheck.  They are execution-wrapper failures and do not
contradict the offline obstacle result.  The final bounded stopping rule was
therefore applied and no further retry was authorized.

\section{Limitations}

The mechanical response of the corrected checkpoint under re-equilibrated
actual history remains unknown.  Consequently, the present evidence does not
establish mechanical continuity after correction, actual-history KKT validity
after equilibration, or an accepted continuation state.  It also provides no
basis for conclusions concerning phase release, D3E, peak load, post-peak
response, or crack-path evolution.

The unresolved checkpoint response is an execution-validation limitation, not
evidence that the offline active-set correction failed.  The corrected package
is retained as a mathematically admissible candidate state, but not as a
validated mechanical restart state.

\section{Future Work}

Any future continuation of this route requires a new execution decision rather
than a scientific-parameter correction.  A replacement workflow should
separate login-side repository checks from compute-node validation, bind every
required executable explicitly after module loading, and qualify the
environment independently before another Abaqus submission.  Until such a
decision is made, full checkpoint hold, phase release, continuation, D3E, and
tolerance changes remain prohibited.
