\chapter{State Transfer and Active-Set Evolution}
\label{chap:stage-d-synthesis}

\section{Controlled Transfer and Abaqus Ingestion}

Stage D began with a controlled analytical transfer between nonmatching meshes.
All target nodes and integration points were mapped deterministically and the
transferred fields remained finite and bounded.  The measured nodal phase
\(L_2\) and maximum errors were \(2.7037\times10^{-2}\) and
\(8.4997\times10^{-2}\); the corresponding history errors were
\(1.0797\times10^{-2}\) and \(2.3398\times10^{-2}\).  These values are retained
as an error baseline rather than described as negligible.

The D2A Abaqus test then proved ingestion of transferred phase and history
through the visualization-layer state variables.  D2B proved a bounded serial
continuation after one documented increment-limit correction.  D2C repeated
the accepted continuation with one MPI rank and four threads.  State fields,
reaction history, energy, and increment sequence were identical to the serial
reference within the recorded comparison precision.

\section{Nonmatching Fracture Checkpoint}

The D3 route transferred a pre-peak checkpoint at
\(U_2=0.003000000026077032\,\mathrm{mm}\) to a nonmatching split-notch mesh
with 6,601 nodes, 6,400 physical elements, and 25,600 integration points.
Package validation established complete coverage, zero unmapped state records,
and no non-positive Jacobians.  The R4 compatible release-hold job
\texttt{1377471.mmaster02} then proved nonmatching state ingestion,
checkpoint equilibration, actual-history KKT consistency, irreversible
active-set release, and state retention through the bounded hold.  Maximum
SDV15 and SDV16 transfer errors were \(1.3878\times10^{-17}\) and zero;
relative RF and energy release jumps were \(2.2926\times10^{-4}\) and
\(1.2746\times10^{-5}\).

\section{Active-Set Evolution}

The fixed R4 active set was tested under a short continuation segment in D3D.
The first invalid state was already the segment initial frame: 30 active
multipliers were below the fixed threshold \(-10^{-8}\).  The count increased
to 3,157 nodes by the endpoint.  Thus, a fixed active set through further
loading was disproven within the tested segment even though free residual,
irreversibility, lower-bound, and Jacobian checks remained valid.

An offline primal--dual correction at the unchanged checkpoint used the
recovered F3 phase as lower bound and actual F3 history without modification.
It converged in seven iterations to 6,374 active and 227 free nodes.  All 30
initial seeds and 42 additional nodes were released, with no reactivation.
The free residual was \(2.1176\times10^{-21}\), the minimum active multiplier
was \(-9.99696\times10^{-9}\), active-bound error was zero, and the phase
functional decreased.  This proves mathematical admissibility under frozen F3
history.

\section{Mechanical-Restart Limitation}

The corrected candidate is not an accepted mechanical restart.  Three bounded
qualification jobs stopped before Abaqus because of execution-wrapper
environment failures: a platform-dependent checksum, Python syntax unsupported
by the default compute-node interpreter, and unavailable \texttt{git} after
module loading.  Mechanical re-equilibration and actual-history KKT
reassessment were therefore not performed.  The mechanical checkpoint
response remains unknown, and no phase release, D3E, peak/post-peak, crack-path,
or online-remeshing conclusion is drawn.

\section{Claim Summary}

\begin{table}[htbp]
\centering
\caption{Stage D evidence and claim boundary.}
\label{tab:stage-d-claims}
\begin{tabular}{p{0.52\linewidth}p{0.38\linewidth}}
\hline
Result & Status \\
\hline
Controlled field transfer & proven \\
Abaqus state ingestion & proven \\
Serial continuation after transfer & proven \\
Four-thread repeatability & proven within tested scope \\
Nonmatching checkpoint transfer & proven within bounded pre-peak scope \\
R4 release hold & proven \\
Fixed active set through further loading & disproven \\
Offline active-set correction & proven under frozen F3 history \\
Corrected mechanical restart & unproven \\
Online remeshing continuation & not claimed \\
D3E/post-peak continuation & not performed \\
\hline
\end{tabular}
\end{table}
