% Thesis chapter draft: Stage C offline refinement demonstration.
\chapter{Offline MISESERI Pre-Refinement for Layered Phase-Field UEL Models}
\label{ch:stage-c-offline-refinement}

\section{Objective}
Demonstrate a custom, auxiliary-continuum, MISESERI-driven offline pre-refinement
workflow for the Molnar layered phase-field UEL model, targeting the elastic,
pre-peak and peak RF--U response of uniform H1 with fewer physical elements.

\section{Method summary}
\begin{enumerate}
  \item Solve an auxiliary continuum pre-analysis with active MISESERI output.
  \item Mark elements with
  \[
    \frac{\mathrm{MISESERI}}{\max(\mathrm{MISESERI})}
    > \texttt{relative\_MISESERI\_threshold},\qquad
    \texttt{relative\_MISESERI\_threshold}=0.05.
  \]
  \item Build a localized graded physical mesh (min size $0.0025\,\mathrm{mm}$,
  max size $0.025\,\mathrm{mm}$, one pass, no coarsening).
  \item Reconstruct U1/U2/CPS4 layers and Fortran \texttt{N\_ELEM}.
  \item Solve with four OpenMP threads and compare to uniform H1.
\end{enumerate}

\section{Verification narrative}
A failed iteration (C2F-v2) omitted the exact $y=0$ mesh line, so notch free faces
were not reconstructed. The resulting continuous plate elevated initial stiffness
by about $72\%$ and suppressed softening. Geometry audit, restoration of $y=0$,
elastic probe ($0.083\%$ stiffness error), phase-field spatial check, and C2F-v3
restored peak/pre-peak agreement with H1.

\section{Results (C2F-v3)}
Peak force difference $0.24\%$; initial stiffness difference $0.061\%$;
pre-peak NRMSE $0.089\%$; peak displacement identical at $0.0058\,\mathrm{mm}$;
$10290$ physical elements ($14.7\%$ fewer than H1). A direct repeat solve,
job \texttt{1376595.mmaster02}, reproduced the frozen C2F-v3 RF--U metrics
exactly at the reporting precision: peak-force relative difference, pre-peak
NRMSE, and initial-stiffness relative difference were all zero against the
original job \texttt{1376480.mmaster02}. The final SDV15 field summary was also
unchanged, with $41160$ finite samples, $2247$ samples above $0.5$, and $464$
samples above $0.95$.

The fair four-thread comparison is now available from the H1 closeout job
\texttt{1376594.mmaster02}. Both H1 and C2F-v3 used four OpenMP threads. Relative
to the four-thread H1 baseline, C2F-v3 used $14.7\%$ fewer physical elements,
$16.7\%$ less walltime, $14.9\%$ less CPU time, and $22.2\%$ less peak memory.
These cost reductions support the efficiency demonstration, but they should not
be attributed solely to remeshing without controlling for all queue, node, module,
and output settings.

Post-peak RF--U equivalence remains limited: the post-peak NRMSE is about $24\%$.
The matched-state SDV15 extraction and crack-path metrics jobs
\texttt{1376596.mmaster02} and \texttt{1376597.mmaster02} completed successfully.
They support C2F-v3 repeatability, but the quantitative H1-versus-refined crack
path comparison is classified as \texttt{crack\_path\_deviation\_detected}. At
$U=0.007\,\mathrm{mm}$ and threshold SDV15 $\geq 0.5$, H1 reaches an extension of
$0.5075\,\mathrm{mm}$ whereas C2F-v3 reaches $0.4949\,\mathrm{mm}$; the Hausdorff
distance is about $0.0122\,\mathrm{mm}$. Therefore the refined model is supported
for elastic, pre-peak, and peak RF--U response, but not as a crack-path-equivalent
replacement for H1.

\section{Production policy}
Uniform H1 remains the production and report reference. The refined mesh is a
demonstration of offline pre-refinement efficiency, not a replacement of H1.
Fair walltime comparisons should use the four-thread H1 closeout package and the
frozen C2F-v3 job records. The automation smoke job \texttt{1376598.mmaster02}
completed with scheduler \texttt{Exit\_status=12}; it is retained as failed guard
evidence and is not used as a scientific result.
