% Thesis chapter draft: Stage D controlled state transfer.
\chapter{Controlled State Transfer for Phase-Field UEL Workflows}
\label{ch:stage-d-state-transfer}

\section{Objective}
Stage D tests whether phase-field and history values transferred between meshes
are actually ingested by Abaqus and routed through the UEL/UMAT state arrays.
The test is intentionally separated from fracture evolution. No interrupted
Molnar fracture simulation is allowed until the D2 ingestion, continuation,
thread-repeatability, and output-routing gates pass.

\section{D1 analytical baseline}
The D1 harness established deterministic and physically guarded transfer
mechanics, but it did not prove negligible transfer error. The retained D1
baselines are:

\begin{table}[h]
\centering
\begin{tabular}{@{}lr@{}}
\toprule
Quantity & Value \\
\midrule
Nodal $d$ L2 error & $0.0270$ \\
Nodal $d$ maximum error & $0.0850$ \\
Integration-point $H$ L2 error & $0.0108$ \\
Integration-point $H$ maximum error & $0.0234$ \\
Energy difference & $-0.00769$ \\
\bottomrule
\end{tabular}
\end{table}

\section{D2A ingestion design}
D2A uses the prepared tiny nonmatching transfer package under
\texttt{models/state\_transfer/d2\_tiny\_transfer/}. A separate D2-only
UEL/UMAT source variant is generated under
\texttt{src/state\_transfer/d2\_tiny\_transfer\_uel.for}; the frozen Molnar
source and accepted C2C-v3 mesh are not modified.

The preserved Molnar U1 user-element card declares phase on Abaqus DOF~3. D2A
therefore prescribes every transferred nodal phase value on DOF~3. History
values are loaded from a generated read-only table keyed by physical element
label and integration point number, initialized once, and mirrored to
visualization \texttt{SDV16}. The interpolated phase value is mirrored to
\texttt{SDV15}.

\section{Current status}
The executable D2A package passed on HPC job \texttt{1376785.mmaster02}. The
PBS exit status was zero, the Abaqus solve completed successfully, the ODB was
readable, and \texttt{D2A.ok} was written. Target element/IP coverage was
$1.0$, the maximum \texttt{SDV15} interpolation error was $0.0$, and the
maximum \texttt{SDV16}/$H$ error was
$6.428999999030793\times10^{-9}$.

Abaqus did not expose the UEL phase DOF as usable nodal \texttt{U} output in
this smoke deck. The accepted D2A proof is therefore the element/IP UMAT mirror:
\texttt{SDV15} proves transferred phase ingestion, and \texttt{SDV16} proves
transferred history ingestion. This is an ingestion and routing verification,
not a fracture-response benchmark.

\section{D2B continuation attempt}
D2B was submitted once as serial PBS job \texttt{1376819.mmaster02}. It did
not pass. Abaqus compiled the D2-only user subroutine and entered the three-step
deck, but the tiny mechanical continuation terminated with solver exit $1$ and
PBS \texttt{Exit\_status=10}. The message file reports
\texttt{TOO MANY INCREMENTS NEEDED TO COMPLETE THE STEP}. Therefore no
\texttt{D2B.ok} marker exists, and no serial state-persistence acceptance claim
is made from this attempt.

The prepared corrective deck increases the release and continuation step
increment allowance to \texttt{inc=50}. It leaves the transferred phase values,
history values, transfer table, label mapping, and D2-only UEL/UMAT state route
unchanged.

\section{D2B accepted rerun}
The corrected D2B rerun, \texttt{1376825.mmaster02}, passed with PBS exit
status zero, solver exit zero, readable ODB output, and classification
\texttt{stage\_d2b\_serial\_continuation\_pass}. The target element/IP
coverage was $1.0$. The maximum initial differences from accepted D2A were
$0.0$ for both \texttt{SDV15} and \texttt{SDV16}; the maximum release
differences were also $0.0$. The final continuation frame reached
$U_2=1.0\times10^{-5}\,\mathrm{mm}$ with finite \texttt{RF2}
$=3.46317381026\times10^{-7}$. The reported \texttt{ALLWK} continuation jump was
$1.2830926425511091\times10^{-11}$; no energy-jump acceptance tolerance is
assigned at D2B.

The rerun wrote \texttt{D2B\_R1.ok}, and the canonical \texttt{D2B.ok} marker
records the accepted rerun job ID.

\section{D2C four-thread repeatability}
The D2C job, \texttt{1376831.mmaster02}, reused the accepted D2B transfer deck
with no physics, transfer-table, mesh, label, step, increment-control, or target
displacement changes. The only execution change was from one serial thread to
\texttt{cpus=4}, \texttt{mp\_mode=threads}, and four OpenMP threads. The Abaqus
message output confirmed \texttt{1 MPI RANK x 4 THREAD}.

D2C passed with PBS exit status zero, solver exit zero, readable ODB output, and
classification \texttt{stage\_d2c\_thread\_repeatability\_pass}. Against the
D2B serial reference, the maximum \texttt{SDV15} and \texttt{SDV16}
thread--serial differences were both $0.0$, target element/IP coverage was
$1.0$, the final $U_2$ difference was $0.0\,\mathrm{mm}$, the final
\texttt{RF2} absolute and relative differences were both $0.0$, the RF--U NRMSE
was $0.0$, and the final-frame \texttt{ALLWK} absolute difference was $0.0$.
The accepted and cutback increment sequence was unchanged.

D2D ABAQUSER output-route verification is the next controlled gate.

\section{D2D0 ABAQUSER availability}
The D2D0 login-node audit did not find an ABAQUSER executable, module, source
implementation, or documented runnable interface. The audit therefore classified
D2D as \texttt{stage\_d2d\_blocked\_abaquser\_not\_found}. This is an
external-tool availability block, not a failure of D1--D2C state transfer. A
normal Abaqus Python extractor is not an acceptable substitute for ABAQUSER
verification.

The first interrupted fracture-transfer experiment has been prepared only as a
design, using a small H0 diagnostic model and an early pre-peak checkpoint near
$U=0.003\,\mathrm{mm}$. No D2D PBS job or interrupted fracture solver job has
been submitted.

\section{D3A existing H0 checkpoint audit}
The existing accepted H0 ODB from job \texttt{1376154.mmaster02} was tested as
the D3 checkpoint source. A CAE/ODB-only extraction selected the frame at
$U_2=0.003000000026077032\,\mathrm{mm}$ and extracted 15720 element/IP state
rows with full coverage, finite \texttt{SDV15}/\texttt{SDV16}, maximum
$d=0.08412302285432816$, maximum $H=0.0512588769197464$, checkpoint
\texttt{RF2} $=0.39450356364250183$, and
\texttt{RF2}/\texttt{RF2}_{\mathrm{peak,H0}}=0.5421925638518931$.

The source ODB lacks \texttt{ALLIE}, \texttt{ALLSE}, and \texttt{ALLWK} global
energy history outputs, so D3A required independent energy evidence before
acceptance. That original blocker is preserved in the history and resolved by
the D3A-E R1 reconstruction.

\section{D3A-E independent energy reconstruction}
D3A-E replaced unavailable global ODB energy history with an independent
quadrature reconstruction from the accepted H0 checkpoint exports. R0 job
\texttt{1376885.mmaster02} is preserved as failed evidence with classification
\path{stage_d3a_energy_reconstruction_fail_parser_scope}; the first parser
mixed \texttt{Part-1} mesh nodes and assembly reference-point nodes into one
namespace.

R1 corrected the parser scope and passed with classification
\path{stage_d3a_energy_reconstruction_pass}: 3930 physical elements, 15720
integration points, non-positive detJ count 0, minimum detJ
$2.829135024804933\times10^{-6}$, and relative energy residual
$0.012586306767288707$. D3A is now closed as
\path{stage_d3a_checkpoint_pass_independent_energy_reconstruction}; D3A2
nonmatching package construction is the next local gate.

\section{D3A2 nonmatching package}
D3A2 built and validated one deterministic nonmatching split-notch target
package locally, without PBS submission. The accepted package classification is
\path{stage_d3a2_transfer_package_pass}. The source is job
\texttt{1376154.mmaster02} at checkpoint
$U_2=0.003000000026077032\,\mathrm{mm}$.

The target has 6601 nodes, 6400 Q4 physical elements, and 25600 integration
points. Its open notch runs from $x=-0.5$ to $x=0.0$ on $y=0$, with 40
duplicated coincident face-node pairs and a shared notch tip. The topology audit
found notch length $0.5\,\mathrm{mm}$, zero crossing elements, and zero
non-positive Jacobian determinants. The transfer package gives target-node and
target-IP coverage 1.0, predicted energy relative jump
$0.015379624558651227$, and unmapped state count 0. The package marker records
\texttt{solver\_job\_submitted=false}; D3A3 ingestion/equilibration/release hold
is the next gate before any continuation solve.

\section{D3A3 ingestion hold attempt}
The first D3A3 full-target ingestion/equilibration/release-hold job,
\texttt{1377382.mmaster02}, was submitted exactly once from the committed D3A2
package after static preflight passed. The job failed before solver analysis:
Abaqus checked out a Standard license, but user-subroutine compilation could
not find \texttt{ifort} because the batch script loaded only
\texttt{abaqus/2023}. The preserved classification is
\path{stage_d3a3_solver_fail_compiler_environment}; no \texttt{D3A3.ok} marker
exists and continuation stages D3D and D3E remain blocked.

D3A3-R1 applied this compiler-environment correction as job
\texttt{1377383.mmaster02}. The environment gate passed: the job recorded
\texttt{gcc/11.4.0}, \texttt{intel/2024.2.0}, \texttt{abaqus/2023}, and a
valid \texttt{ifort}. The analysis still did not start because the generated
\texttt{d3\_transfer\_table.inc} exceeded the Intel Fortran statement token
limit during user-subroutine compilation. The classification is
\path{stage_d3a3_solver_fail_transfer_table_compile}; no \texttt{D3A3\_R1.ok}
or \texttt{D3A3.ok} marker exists, so D3D and D3E remain blocked.

D3A3-R2 is prepared as a compile/datacheck gate only. It keeps the R0 and R1
evidence directories unchanged and moves the new compile evidence to
\path{runs/hpc/stage_d3/interrupted_transfer/target_ingestion_compile_r2/}.
The oversized compile-time transfer include is replaced by a headerless runtime
\path{d3_transfer_h.dat} file loaded once through \texttt{UEXTERNALDB}, while
the physical Molnar H0 UEL/UMAT source remains the base implementation. Local
runtime-state validation passed for 25600 H records, with minimum $H$
$1.0045788889553414\times10^{-8}$, maximum $H$
$0.027317036782803523$, and SHA256
\texttt{4689ea5c10c0972e69ba46f8676a326c8b011b98faa8031c7c26cfb218607cd9}.
The R2 static validation classification is
\path{stage_d3a3_static_validation_pass}. The compile/datacheck job
\texttt{1377389.mmaster02} compiled and linked the user subroutine and
completed input processing, showing that the R1 compile-token problem was
removed. Standard datacheck then failed because \texttt{UEXTERNALDB} opened
relative file \path{d3_transfer_h.dat} from Abaqus' internal \path{/local/...}
work directory where the file had not been staged. The classification is
\path{stage_d3a3_r2_datacheck_fail_runtime_h_file_not_in_abaqus_workdir}. No
\texttt{D3A3\_R2\_COMPILE.ok} marker exists, no full D3A3-R2 solver job has
been submitted, and D3D/D3E remain blocked.

The bounded D3A3-R2-R1 correction then ran as job
\texttt{1377391.mmaster02}. It changed only the runtime-H file location logic:
\texttt{UEXTERNALDB} calls \texttt{GETOUTDIR}, constructs
\texttt{OUTDIR//'/d3\_transfer\_h.dat'}, prints the resolved
path, and opens \texttt{FILE=HFILE(1:LHFILE)}. The path audit passed and the
runtime-H SHA256 remained
\texttt{4689ea5c10c0972e69ba46f8676a326c8b011b98faa8031c7c26cfb218607cd9}.
The prior \path{/local/...} missing-file failure was removed: Standard reported
the staged \path{/scratch9/.../d3_transfer_h.dat} path. Datacheck then failed
with Intel Fortran severe (24), end-of-file during read on unit 99. The
classification is
\path{stage_d3a3_r2_r1_datacheck_fail_runtime_h_eof_after_getoutdir_open}. No
\texttt{D3A3\_R2\_COMPILE.ok} marker exists, no full D3A3-R2 solver job has
been submitted, and D3D/D3E remain blocked.

D3A3-R2-R2 is prepared as the next bounded compile/datacheck correction. It
keeps the R2-R1 \texttt{GETOUTDIR} runtime-file path but replaces the
EOF-driven runtime-H loader with an exact counted loop over
\texttt{N\_ELEM*NIP}=25600 records. The generated source rejects the old
\texttt{GOTO 100} loop, uses explicit premature-EOF and read-error branches,
keeps post-read count and key-coverage checks, and prints
\texttt{D3A3-R2 H LOAD COMPLETE} only after all records are loaded. The static
audit classification is
\path{stage_d3a3_r2_r2_counted_read_audit_pass}; it records no physics, mesh,
input-deck, runtime-H, material, weak-form, layer-offset, step-definition, or
checkpoint-U2 change. Evidence is staged under
\path{runs/hpc/stage_d3/interrupted_transfer/target_ingestion_compile_r2_r2/}.
Until the single counted-read datacheck passes and
\texttt{D3A3\_R2\_COMPILE.ok} is committed, no full D3A3-R2, D3D, or D3E job is
authorized.
