% Stage D2 state-ingestion report snippet.
\documentclass[11pt,a4paper]{article}
\usepackage[margin=25mm]{geometry}
\usepackage{booktabs}
\usepackage{hyperref}
\title{Stage D2: Minimal Abaqus State-Ingestion Verification}
\author{Adaptive Remeshing Thesis}
\date{2026-07-22}
\begin{document}
\maketitle

\section{Status}
The D2A executable package and HPC ingestion job passed with classification
\path{stage_d2a_state_ingestion_pass}. The accepted PBS job was
\texttt{1376785.mmaster02}; it finished with PBS \texttt{Exit\_status=0},
solver exit zero, readable ODB output, and a written \texttt{D2A.ok} marker.

\section{D1 transfer-error baselines}
\begin{table}[h]
\centering
\begin{tabular}{@{}lr@{}}
\toprule
Quantity & Value \\
\midrule
Nodal $d$ L2 error & $0.0270$ \\
Nodal $d$ maximum error & $0.0850$ \\
IP $H$ L2 error & $0.0108$ \\
IP $H$ maximum error & $0.0234$ \\
Energy difference & $-0.00769$ \\
\bottomrule
\end{tabular}
\end{table}

\section{D2A route}
The D2A source variant confirms the preserved Molnar U1 phase DOF as DOF~3 and
uses a generated element/IP keyed table for transferred history initialization.
The tiny target contains $15$ target nodes, $8$ physical elements, and one
visualization integration point per physical element. The phase nodes use
labels $1$--$15$, while the mechanics and visualization nodes are duplicated as
labels $1001$--$1015$. The U1 layer uses element labels $1$--$8$, the U2 layer
uses $9$--$16$, and the visualization layer uses $17$--$24$.

\section{Accepted result}
\begin{table}[h]
\centering
\begin{tabular}{@{}lr@{}}
\toprule
Quantity & Value \\
\midrule
Job ID & \texttt{1376785.mmaster02} \\
PBS exit status & $0$ \\
Target element/IP coverage & $1.0$ \\
Maximum \texttt{SDV15} interpolation error & $0.0$ \\
Maximum \texttt{SDV16}/$H$ error & $6.428999999030793\times10^{-9}$ \\
Failures & $0$ \\
\bottomrule
\end{tabular}
\end{table}

The ODB comparison verifies transferred phase ingestion through the UMAT mirror
\texttt{SDV15}, which equals the independent interpolation of transferred nodal
phase on every target element/IP. It verifies transferred history ingestion
through \texttt{SDV16}, which matches transferred $H$ within the $10^{-8}$
tolerance. Abaqus did not expose the UEL phase DOF as usable nodal
\texttt{U} output in this smoke deck, so nodal \texttt{U} is recorded as an ODB
output limitation rather than as the accepted phase-ingestion signal.

\section{D2B Serial Continuation}
The first serial continuation job, \texttt{1376819.mmaster02}, is preserved as
\path{stage_d2b_solver_fail_increment_limit}. Initialization and release
completed, but the tiny continuation partially converged and then exhausted the
maximum increment count. No scientific state-persistence acceptance claim is
made from that failed attempt.

The corrected rerun, \texttt{1376825.mmaster02}, changed only the maximum
increment allowance in the D2B release and continuation steps from
\texttt{inc=2} to \texttt{inc=50}. It passed with classification
\path{stage_d2b_serial_continuation_pass}. The transfer values, transfer table,
element/IP labels, mesh, boundary-condition definitions, tiny displacement,
static step data, serial execution mode, and D2-only UEL/UMAT route were
unchanged.

\begin{table}[h]
\centering
\begin{tabular}{@{}lr@{}}
\toprule
Quantity & Value \\
\midrule
Job ID & \texttt{1376825.mmaster02} \\
PBS exit status & $0$ \\
Solver exit & $0$ \\
Target element/IP coverage & $1.0$ \\
Maximum initial \texttt{SDV15}/\texttt{SDV16} difference & $0.0$ \\
Maximum release \texttt{SDV15}/\texttt{SDV16} difference & $0.0$ \\
Final prescribed $U_2$ & $1.0\times10^{-5}$ mm \\
Final \texttt{RF2} & $3.46317381026\times10^{-7}$ \\
\texttt{ALLWK} continuation jump & $1.2830926425511091\times10^{-11}$ \\
Accepted marker & \texttt{D2B\_R1.ok} and canonical \texttt{D2B.ok} \\
\bottomrule
\end{tabular}
\end{table}

Energy quantities are reported for D2B, but no arbitrary energy-jump tolerance
is assigned at this stage.

\section{D2C Four-Thread Repeatability}
The D2C job, \texttt{1376831.mmaster02}, reran the accepted transferred-state
continuation using \texttt{cpus=4}, \texttt{mp\_mode=threads}, and
\texttt{OMP\_NUM\_THREADS=4}. The accepted D2B R1 job
\texttt{1376825.mmaster02} was used as the frozen serial reference. The input
deck differed from D2B only in the heading comment; the transfer table, source,
mesh, labels, step definitions, \texttt{inc=50} controls, and
$U_2=1.0\times10^{-5}$ mm target displacement were unchanged.

\begin{table}[h]
\centering
\begin{tabular}{@{}lr@{}}
\toprule
Quantity & Value \\
\midrule
Job ID & \texttt{1376831.mmaster02} \\
PBS exit status & $0$ \\
Solver exit & $0$ \\
Thread confirmation & \texttt{1 MPI RANK x 4 THREAD} \\
Target element/IP coverage & $1.0$ \\
Maximum \texttt{SDV15} thread--serial difference & $0.0$ \\
Maximum \texttt{SDV16} thread--serial difference & $0.0$ \\
Final $U_2$ difference & $0.0$ mm \\
Final \texttt{RF2} absolute/relative difference & $0.0$ / $0.0$ \\
\texttt{RF--U} NRMSE & $0.0$ \\
Final-frame \texttt{ALLWK} absolute difference & $0.0$ \\
Increment sequence changed & \texttt{false} \\
Accepted marker & \texttt{D2C.ok} \\
\bottomrule
\end{tabular}
\end{table}

D2C therefore passes as a shared-state/thread-safety repeatability check. The
next controlled gate is D2D ABAQUSER output-route verification.

\section{D2D0 ABAQUSER Availability Audit}
D2D0 was performed on the login node without submitting a PBS job. The audit
checked executable lookup, module discovery, local filesystem matches, and
repository references for ABAQUSER. No usable ABAQUSER executable, module,
source implementation, or documented runnable interface was found. The only
filesystem match was the guarded D2D PBS placeholder.

The D2D0 classification is
\path{stage_d2d_blocked_abaquser_not_found}. D2D is therefore blocked by
external tool availability, not by a failed state-transfer comparison. D1--D2C
remain valid. A normal Abaqus Python extractor must not be substituted and
reported as ABAQUSER verification.

\section{D3A Existing H0 Checkpoint Audit}
The existing H0 ODB from job \texttt{1376154.mmaster02} was audited as a
possible early pre-peak D3 checkpoint source. The corrected CAE/ODB-only
extraction attempt, \texttt{1376879.mmaster02}, selected the frame at
$U_2=0.003000000026077032\,\mathrm{mm}$ without state interpolation. It
extracted 15720 element/IP rows with target coverage $1.0$, finite
\texttt{SDV15}/\texttt{SDV16}, maximum $d=0.08412302285432816$, maximum
$H=0.0512588769197464$, checkpoint \texttt{RF2}
$=0.39450356364250183$, and \texttt{RF2}/H0 peak
$=0.5421925638518931$.

The source ODB lacks the required \texttt{ALLIE}, \texttt{ALLSE}, and
\texttt{ALLWK} global energy history outputs, so D3A required independent
energy evidence before acceptance. That original blocker is preserved in the
history, but it is resolved by the scope-corrected D3A-E R1 reconstruction.

\section{D3A-E Independent Energy Reconstruction}
D3A-E froze an independent quadrature-based energy-evidence route instead of
rerunning the H0 fracture model merely to request global Abaqus energy output.
R0 job \texttt{1376885.mmaster02} is preserved as failed evidence with
classification \path{stage_d3a_energy_reconstruction_fail_parser_scope}; the
first parser mixed \texttt{Part-1} node labels with the assembly reference-point
namespace.

R1 corrected the parser scope and passed with classification
\path{stage_d3a_energy_reconstruction_pass}: 3930 physical elements, 15720
integration points, non-positive detJ count 0, minimum detJ
$2.829135024804933\times10^{-6}$, and relative energy residual
$0.012586306767288707$. D3A is closed as
\path{stage_d3a_checkpoint_pass_independent_energy_reconstruction}. The
\texttt{D3A.ok} marker exists, and D3A2 package construction is the next local
gate before any fracture solver job.

\section{D3A2 and D3A3 Status}
D3A2 built a deterministic nonmatching split-notch transfer package with 6601
target nodes, 6400 Q4 physical elements, and 25600 target integration points.
The split-notch audit found 40 duplicated open-face node pairs, a shared notch
tip, notch length $0.5\,\mathrm{mm}$, zero crossing elements, and zero
non-positive Jacobian determinants. The package passed with target-node and
target-IP coverage 1.0, predicted energy relative jump
$0.015379624558651227$, and unmapped state count 0.

The first D3A3 full-target ingestion/equilibration/release-hold job,
\texttt{1377382.mmaster02}, was submitted exactly once after static preflight.
It failed before solver analysis because the batch environment loaded only
\texttt{abaqus/2023}; Abaqus user-subroutine compilation could not find
\texttt{ifort}. The preserved classification is
\path{stage_d3a3_solver_fail_compiler_environment}. No \texttt{D3A3.ok} marker
exists, and D3D/D3E remain blocked.

D3A3-R1 applied that bounded compiler-environment correction as job
\texttt{1377383.mmaster02}. The compiler environment passed: the job recorded
\texttt{gcc/11.4.0}, \texttt{intel/2024.2.0}, \texttt{abaqus/2023}, and a
valid \texttt{ifort}. The job still failed before solver analysis because
\texttt{d3\_transfer\_table.inc} exceeded the Intel Fortran statement token
limit during user-subroutine compilation. The classification is
\path{stage_d3a3_solver_fail_transfer_table_compile}. No \texttt{D3A3\_R1.ok}
or canonical \texttt{D3A3.ok} marker exists, and D3D/D3E remain blocked.

D3A3-R2 is prepared only as a compile/datacheck gate. It preserves the R0 and
R1 evidence directories and records new compile-gate evidence under
\path{runs/hpc/stage_d3/interrupted_transfer/target_ingestion_compile_r2/}.
The correction replaces the oversized compile-time DATA include with a
headerless runtime \path{d3_transfer_h.dat} file loaded once through
\texttt{UEXTERNALDB}. The runtime file validates locally with 25600 records,
minimum $H=1.0045788889553414\times10^{-8}$, maximum
$H=0.027317036782803523$, and SHA256
\texttt{4689ea5c10c0972e69ba46f8676a326c8b011b98faa8031c7c26cfb218607cd9};
the static preflight classification is \path{stage_d3a3_static_validation_pass}.
The compile/datacheck job \texttt{1377389.mmaster02} compiled and linked the
user subroutine and completed input processing, which resolves the R1
compile-token failure. Standard datacheck then failed because
\texttt{UEXTERNALDB} opened relative file \path{d3_transfer_h.dat} from
Abaqus' internal \path{/local/...} work directory where the file had not been
staged. The classification is
\path{stage_d3a3_r2_datacheck_fail_runtime_h_file_not_in_abaqus_workdir}. No
\texttt{D3A3\_R2\_COMPILE.ok} marker exists, no full D3A3-R2 solver job has
been submitted, and D3D/D3E remain blocked.

The bounded D3A3-R2-R1 correction ran as job \texttt{1377391.mmaster02}. It
replaces the relative \path{d3_transfer_h.dat} open with \texttt{GETOUTDIR} and
\texttt{HFILE(1:LHFILE)}. The path audit records no physics, mesh, input deck,
checkpoint displacement, material, or runtime-H value change, and passes as
\path{stage_d3a3_r2_r1_path_audit_pass}. The runtime-H SHA256 remains
\texttt{4689ea5c10c0972e69ba46f8676a326c8b011b98faa8031c7c26cfb218607cd9}.
The prior \path{/local/...} missing-file failure was removed because Standard
reported the staged \path{/scratch9/.../d3_transfer_h.dat} path, but datacheck
then failed with Intel Fortran severe (24), end-of-file during read on unit 99.
The classification is
\path{stage_d3a3_r2_r1_datacheck_fail_runtime_h_eof_after_getoutdir_open}. No
\texttt{D3A3\_R2\_COMPILE.ok} marker exists, no full D3A3-R2 solver job has
been submitted, and D3D/D3E remain blocked.

D3A3-R2-R2 is prepared as the bounded counted-read correction. It keeps the
R2-R1 \texttt{GETOUTDIR} path construction and changes only the runtime-H
reader: the old EOF-driven loop is replaced by an exact
\texttt{DO IREC=1,N\_ELEM*NIP} loop over 25600 records, with explicit
premature-EOF and read-error exits and the existing count and key-coverage
checks retained. The static audit rejects the old \texttt{GOTO 100} loader,
requires \texttt{END=900}, \texttt{ERR=910}, and
\texttt{D3A3-R2 H LOAD COMPLETE}, and passes as
\path{stage_d3a3_r2_r2_counted_read_audit_pass}. It records no physics, mesh,
input-deck, runtime-H, material, weak-form, layer-offset, step-definition, or
checkpoint-U2 change. Evidence is staged under
\path{runs/hpc/stage_d3/interrupted_transfer/target_ingestion_compile_r2_r2/}.
The login-node \texttt{ifort -extend-source} counted-reader smoke passed with
25600 records, first key $(1,1)$, last key $(6400,4)$, premature EOF false,
read error false, duplicates 0, and missing keys 0.
The single counted-read datacheck ran as job \texttt{1377393.mmaster02} from
commit \texttt{9058534a9daa188d2d958f8462b230ec843c545e}. Abaqus compiled,
linked, completed input processing and Standard datacheck, and printed
\texttt{D3A3-R2 H LOAD COMPLETE 25600}; premature-EOF and runtime-H read-error
tokens are absent. The PBS wrapper nevertheless exited with
\texttt{Exit\_status=10} because Abaqus wrapped the long \texttt{GETOUTDIR}
path across two \texttt{.msg} lines before the \texttt{.mmaster02} suffix, and
the exact full-path grep failed. The preserved classification is
\path{stage_d3a3_r2_r2_datacheck_fail_pbs_path_gate_linewrap_false_negative}.
A deterministic no-PBS login-node postcheck replay reconstructed the wrapped
path as
\path{/scratch9/pr21vyci/adaptive-remeshing/runs/d3a3_r2_datacheck_r2_1377393.mmaster02/d3_transfer_h.dat}
and rechecked the preserved compiler, link, input-processing, Standard
datacheck, runtime-H, and failure-analysis evidence. The replay preserves the
original PBS \texttt{Exit\_status=10} while classifying the compile/datacheck
scientific gate as
\path{stage_d3a3_r2_compile_datacheck_pass_postcheck_replay}. The replay
created \texttt{D3A3\_R2\_COMPILE.ok} under
\path{runs/hpc/stage_d3/interrupted_transfer/target_ingestion_compile_r2_r2_replay/};
no new PBS datacheck was submitted. No full D3A3-R2, D3D, or D3E job has been
submitted yet; D3D and D3E remain blocked until full D3A3-R2 creates
\texttt{D3A3.ok}.

The full D3A3-R2 ingestion/equilibration/release-hold lane is prepared in new
R2-specific PBS and submit scripts. The lane requires the committed replay
\texttt{D3A3\_R2\_COMPILE.ok}, stages runtime \path{d3_transfer_h.dat},
forbids \path{d3_transfer_table.inc}, uses serial CPU1/16GB/02:00 with
\texttt{OMP\_NUM\_THREADS=1} and \texttt{mp\_mode=threads}, preserves Abaqus
outputs, runs Abaqus-Python extraction, and creates \texttt{D3A3.ok} only after
the strengthened validation gates pass. The deck now requests global nodal
\texttt{U, RF} output so selected frames can be checked using target Q4
bulk-plus-AT2 fracture-energy reconstruction.

The full D3A3-R2 job ran exactly once as \texttt{1377396.mmaster02} from commit
\texttt{7a860f50fe557cd88cd3299dd47b1f260071f3fa}. Abaqus compiled, linked,
completed input processing, completed Standard analysis, and produced an ODB
and extraction outputs. Strengthened validation failed with PBS
\texttt{Exit\_status=21}: \texttt{SDV15} transfer max error
$0.018013543321948218$, \texttt{SDV16} transfer max error
$0.01645326664671945$, checkpoint \texttt{U2} only
$0.0014999968154910865$, RF release jump $1.0292182958543674$, d-healing
violations 4651, maximum phase adjustment $0.013784315224591115$, and missing
phase-node values for reconstructed energy. The classification is
\path{stage_d3a3_r2_full_validation_fail}; no \texttt{D3A3.ok} marker exists,
and D3D/D3E remain blocked.

An ODB-only forensic replay then reprocessed the preserved
\texttt{1377396.mmaster02} ODB without another Abaqus/Standard solve,
Fortran compilation, transfer-package generation, or mesh generation. The
forensic extractor reverses the visualization IP3/IP4 mapping, reads
\texttt{U2}/\texttt{RF2} from the ODB \texttt{TOP} set, and recovers nodal
phase values from corrected \texttt{SDV15} Gauss-point values. Corrected
\texttt{SDV15} transfer max error is $1.3877787807814457\times10^{-17}$,
corrected \texttt{SDV16} transfer max error is $0.0$, the TOP set contains 81
nodes at checkpoint \texttt{U2}=0.003000000026077032, phase recovery returns
6601 nodes and 6400 complete elements, and corrected energy reconstruction has
zero missing phase, \texttt{SDV12}, or \texttt{SDV13} entries. The replay
classification is
\path{stage_d3a3_r2_ingestion_pass_release_not_accepted}; it creates only
\texttt{D3A3\_R2\_INGESTION.ok}. No canonical \texttt{D3A3.ok} marker is
created because d-healing remains 4651 despite zero H decrease violations.
The F1 compatibility residual has L2 norm $3.173013579358624\times10^{-8}$,
maximum residual $1.0654297154470889\times10^{-6}$ at node 3321, and
correlation $-0.7125040883621269$ with released d change.

D3A4 performed the constrained compatibility projection offline from the
forensic evidence. It assembled the sparse target phase system with F1 history
and solved the obstacle problem \(d_\mathrm{compatible}\ge d_\mathrm{F1}\)
without an Abaqus job, Fortran compilation, new transfer package, or new mesh.
The assembly audit covers 6601 nodes, 6400 elements, and 25600 integration
points with zero non-positive Jacobians; it reproduces the forensic F1 residual
with maximum error $2.329340604949326\times10^{-21}$ and the same maximum
residual node 3321. The active-set solve converged in 5 iterations with 1880
active and 4721 free nodes, free residual infinity norm
$7.623296525288703\times10^{-21}$, minimum active multiplier
$3.1903130564656594\times10^{-13}$, and complementarity infinity norm
$8.649244021664495\times10^{-23}$. The compatible field has zero predicted
healing violations, maximum d increase $0.011345805575019186$, normalized L2
increase $0.03901956109385224$, and phase-functional reduction
$2.4132803703716662\times10^{-8}$. The pass classification is
\path{stage_d3a4_constrained_phase_compatibility_pass}; \texttt{D3A4.ok}
exists and a separate
\path{runs/hpc/stage_d3/interrupted_transfer/package_compatible_r1/} package
was prepared. The original package remains unchanged. D3A3-R3, D3D, and D3E
remain unsubmitted.

D3A3-R3 is prepared as a separate compatible active-set lane. The executable
directory is
\path{models/state_transfer/d3_interrupted_transfer/executable_r3_compatible/};
the original executable and D3A2 package are unchanged. The R3 deck prescribes
all 6601 compatible phase values in Steps 1 and 2, then releases only the 4721
free phase nodes in Step 3 while keeping the 1880 D3A4 active nodes fixed at
their lower-bound values. Static validation passes: Step-1 and Step-2 phase
boundary counts are 6601, Step-3 phase boundary count is 1880, Step-3 free-node
phase boundary count is 0, runtime H has 25600 records with no duplicates or
missing keys, obsolete \path{d3_transfer_table.inc} is absent, MPI is absent,
and the UEL source hash is byte-identical to accepted R2. The R3 runtime-H
SHA-256 is
\path{ee244da4e87ff0edb1c6e931fe633921aae552785d2d03efb8d18eea555c7173}.
Only the R3 datacheck is authorized next.

The first R3 datacheck job, \texttt{1377404.mmaster02}, failed before Abaqus
started because \path{executable_r3_compatible/d3_transfer_h.dat} had been
generated locally but remained ignored/untracked. PBS exited with status 6
during runtime-state staging, no Standard datacheck was performed, and no
\texttt{D3A3\_R3\_DATACHECK.ok} marker exists. The corrected preparation now
force-tracks the runtime-H file and the static validation includes
\texttt{runtime\_H\_tracked=true}.

\end{document}
