\documentclass[11pt,a4paper]{article}

\usepackage[margin=25mm]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{array}

\title{Stage A Execution, Failure, and Retry Log\\Adaptive Remeshing Phase-Field Thesis}
\author{Pruthvi Raj Vakkalagadda}
\date{Updated 2026-07-16}

\begin{document}
\maketitle

\section*{Purpose and Maintenance Rule}

\noindent\textbf{Stage:} Stage A\\
\textbf{Document status:} active living document\\
\textbf{Last updated:} 2026-07-16

\medskip

This companion log is the permanent Stage A record of controlled executions, failures, repairs, retries, and classification changes. It complements the high-level Stage A baseline report at \texttt{docs/reports/STAGE\_A\_BASELINE\_REPORT.tex}. Failed attempts remain in this log and are not removed after a repair succeeds. Generated PDFs belong in the ignored build directory and are not evidence substitutes.

During Stage A, every substantial environment, run, validation, failure, repair, retry, figure, table, result, or scientific decision must update both Stage A living documents where relevant. These two files continue until Stage A is formally completed. At Stage A closure, both files should be marked frozen, final conclusions and exit decisions should be added, and a new pair should be opened for Stage B. Do not create a new Stage A report for every run.

\section*{Scientific Boundary}

The records below concern controlled environment and trivial smoke tests only. They do not run, modify, or validate the Molnar benchmark, MISESERI pre-refinement, remeshing, state transfer, multi-CPU execution, or a parameter study. Gate A3 remains:

\begin{center}
\texttt{reference\_data\_insufficient}
\end{center}

The Stage A benchmark and remeshing path therefore remain blocked until the reference route is resolved.

Detailed task, phase, and gate status is maintained in the authoritative living checklist \texttt{docs/project/PROJECT\_PHASE\_CHECKLIST.md}. This log records chronological evidence and diagnostics; it does not duplicate the complete checklist.

\section{Chronological Summary}

\small
\begin{longtable}{@{}p{0.12\linewidth}p{0.20\linewidth}p{0.13\linewidth}p{0.12\linewidth}p{0.16\linewidth}p{0.17\linewidth}@{}}
\caption{Stage A HPC execution and retry summary.}\\
\toprule
Job ID & Purpose & Revision & PBS result & Classification & Evidence \\
\midrule
\endfirsthead
\toprule
Job ID & Purpose & Revision & PBS result & Classification & Evidence \\
\midrule
\endhead
\texttt{1374529.mmaster02} & Environment smoke: PBS, modules, Abaqus visibility, Intel compiler visibility & \texttt{f508a469...} & \texttt{F}, exit 1 & \texttt{hpc\_environment\_smoke\_fail} & \path{runs/hpc/20260715_abaqus_environment_smoke/} \\
\texttt{1374530.mmaster02} & Environment rerun with \texttt{gcc/11.4.0} before Intel & \texttt{f508a469...} & \texttt{F}, exit 127 & \texttt{hpc\_environment\_smoke\_fail} & \path{runs/hpc/20260715_abaqus_environment_smoke_rerun_gcc/} \\
\texttt{1374531.mmaster02} & Final environment rerun with revision supplied via \texttt{PROJECT\_REVISION} & \texttt{d2e9e3c...} & \texttt{F}, exit 0 & \texttt{hpc\_environment\_smoke\_pass} & \path{runs/hpc/20260715_abaqus_environment_smoke_rerun_revision_env/} \\
\texttt{1374532.mmaster02} & Trivial Abaqus/Standard \texttt{UEXTERNALDB} compile-link-license smoke & \texttt{b2db162...} & \texttt{F}, exit 1 & \texttt{hpc\_user\_subroutine\_smoke\_fail} & \path{runs/hpc/20260715_abaqus_user_subroutine_smoke/} \\
\texttt{1374533.mmaster02} & Deterministic \texttt{UEXTERNALDB} callback retry with \texttt{GETOUTDIR} marker & \texttt{c5db808...} & \texttt{F}, exit 0 & \texttt{hpc\_user\_subroutine\_smoke\_pass} & \path{/scratch/pr21vyci/adaptive-remeshing/stage/abaqus_user_subroutine_smoke_retry_1374533.mmaster02/} \\
\bottomrule
\end{longtable}
\normalsize

\section{Job 1374529.mmaster02: Initial Environment Smoke}

\begin{tabularx}{\linewidth}{@{}lX@{}}
\toprule
Field & Value \\
\midrule
Date & 2026-07-15 \\
Approximate output time & 06:34, from preserved run context \\
Purpose & Verify PBS scheduling, compute-node start, scratch creation, module loading, Abaqus visibility, Intel \texttt{ifx} visibility, and repository revision capture. \\
Repository revision & \texttt{f508a469e8247565e3df539346c219b413e492b8} \\
Queue and resources & \texttt{testq}; one node; one CPU; \SI{8}{GB}; 00:30:00 wall time \\
Compute host & \texttt{mnode098.cluster} \\
Scheduler metadata & \texttt{Resource\_List.ngpus = 1} appeared as scheduler metadata; the script did not request or use a GPU. \\
PBS result & \texttt{job\_state = F}; \texttt{Exit\_status = 1} \\
Evidence & \path{runs/hpc/20260715_abaqus_environment_smoke/RUN_SUMMARY.md} \\
\bottomrule
\end{tabularx}

\subsection*{Observed Result}

The job was scheduled and started, assigned one compute host, created scratch, loaded \texttt{intel/2024.2.0} and \texttt{abaqus/2023}, found valid \texttt{abaqus} and \texttt{ifx} executables, and completed \texttt{abaqus information=release}. It failed before the final success marker because \texttt{ifx --version} returned Intel compiler error \texttt{\#10417}; the compiler environment could not set up the required GCC install-path setting.

\subsection*{Classification}

\begin{center}
\texttt{hpc\_environment\_smoke\_fail}
\end{center}

Failure category: HPC compiler-environment setup. Corrective action: load \texttt{gcc/11.4.0} before \texttt{intel/2024.2.0} in the batch environment.

\section{Job 1374530.mmaster02: GCC-First Environment Rerun}

\begin{tabularx}{\linewidth}{@{}lX@{}}
\toprule
Field & Value \\
\midrule
Date & 2026-07-15 \\
Approximate output time & 06:40, from preserved run context \\
Purpose & Verify whether loading \texttt{gcc/11.4.0} before Intel resolves the compute-node \texttt{ifx} initialization failure. \\
Repository revision before submission & \texttt{f508a469e8247565e3df539346c219b413e492b8} \\
Queue and resources & \texttt{testq}; one node; one CPU; \SI{8}{GB}; 00:30:00 wall time \\
Compute host & \texttt{mnode098.cluster} \\
Scheduler metadata & \texttt{Resource\_List.ngpus = 1} appeared as scheduler metadata; the script did not request or use a GPU. \\
PBS result & \texttt{job\_state = F}; \texttt{Exit\_status = 127} \\
Evidence & \path{runs/hpc/20260715_abaqus_environment_smoke_rerun_gcc/RUN_SUMMARY.md} \\
\bottomrule
\end{tabularx}

\subsection*{Observed Result}

The job confirmed PBS execution, compute-node assignment, scratch creation, and progression past the repaired module-loading block. It failed before compiler and Abaqus diagnostics because \texttt{git} was unavailable in the compute-node batch \texttt{PATH} when the script attempted to print the repository revision.

\subsection*{Classification}

\begin{center}
\texttt{hpc\_environment\_smoke\_fail}
\end{center}

Failure category: batch metadata dependency. This was not a PBS, Abaqus, repository, model, MISESERI, or remeshing failure. Corrective action: supply the repository revision from the login/submission environment through \texttt{PROJECT\_REVISION}, avoiding a compute-node Git dependency.

\section{Job 1374531.mmaster02: Final Environment Rerun}

\begin{tabularx}{\linewidth}{@{}lX@{}}
\toprule
Field & Value \\
\midrule
Date & 2026-07-15 \\
Approximate output time & 06:50, from preserved run context \\
Purpose & Final environment-only rerun with repaired module order and revision supplied through \texttt{PROJECT\_REVISION}. \\
Repository revision & \texttt{d2e9e3c0d1e86e5f12772cb3d7e191a5377ea54f} \\
Queue and resources & \texttt{testq}; one node; one CPU; \SI{8}{GB}; 00:30:00 wall time \\
Compute host & \texttt{mnode098.cluster} \\
Scheduler metadata & \texttt{Resource\_List.ngpus = 1} appeared as scheduler metadata; the script did not request or use a GPU. \\
PBS result & \texttt{job\_state = F}; \texttt{Exit\_status = 0} \\
Evidence & \path{runs/hpc/20260715_abaqus_environment_smoke_rerun_revision_env/RUN_SUMMARY.md} \\
\bottomrule
\end{tabularx}

\subsection*{Observed Result}

The job passed the environment acceptance criteria. It loaded \texttt{gcc/11.4.0}, \texttt{intel/2024.2.0}, and \texttt{abaqus/2023}; found valid \texttt{gcc}, \texttt{gfortran}, \texttt{ifx}, and \texttt{abaqus} paths; completed \texttt{gcc --version}, \texttt{gfortran --version}, \texttt{ifx --version}, and \texttt{abaqus information=release}; captured the supplied repository revision; and printed \texttt{Environment smoke probe completed.}

\subsection*{Classification}

\begin{center}
\texttt{hpc\_environment\_smoke\_pass}
\end{center}

Boundary: this pass establishes PBS execution, module loading, compiler visibility, Abaqus executable visibility, scratch setup, and repository revision capture. It does not test Abaqus user-subroutine compilation or linking and does not validate the phase-field formulation.

\section{Job 1374532.mmaster02: Trivial Abaqus/Standard User-Subroutine Smoke}

\begin{tabularx}{\linewidth}{@{}lX@{}}
\toprule
Field & Value \\
\midrule
Date & 2026-07-15 \\
Approximate output time & 07:06, from preserved run context \\
Purpose & Verify Abaqus/Standard license checkout, trivial user-subroutine compilation, linking, solver completion, ODB creation, and \texttt{UEXTERNALDB} callback marker evidence. \\
Repository revision & \texttt{b2db162ff7a4a8cf034c20884323f3f674999e61} \\
Queue and resources & \texttt{testq}; one node; one CPU; \SI{8}{GB}; 00:30:00 wall time \\
Compute host & \texttt{mnode098.cluster} \\
Scheduler metadata & \texttt{Resource\_List.ngpus = 1} appeared as scheduler metadata; the script did not request or use a GPU and called Abaqus with \texttt{cpus=1}. \\
Work directory & \path{/scratch/pr21vyci/adaptive-remeshing/runs/abaqus_user_subroutine_smoke_1374532.mmaster02} \\
Text stage directory & \path{/scratch/pr21vyci/adaptive-remeshing/stage/abaqus_user_subroutine_smoke_1374532.mmaster02} \\
PBS result & \texttt{job\_state = F}; \texttt{Exit\_status = 1} \\
Evidence & \path{runs/hpc/20260715_abaqus_user_subroutine_smoke/} \\
\bottomrule
\end{tabularx}

\subsection*{Observed Result}

The job was scheduled and started. Abaqus/Standard license checkout succeeded, using the preserved evidence that tokens were checked out from Flexnet server \texttt{license4.imfd.tu-freiberg.de}. Fortran compilation succeeded, linking succeeded, the trivial Abaqus/Standard analysis completed successfully, the \texttt{.sta} file contained \texttt{THE ANALYSIS HAS COMPLETED SUCCESSFULLY}, and \texttt{abaqus\_user\_subroutine\_smoke.odb} was present in the scratch work directory.

The required callback marker \texttt{uexternaldb\_smoke.called} was absent. The PBS script therefore stopped at the marker check and did not print the final success marker.

\subsection*{Classification}

\begin{center}
\texttt{hpc\_user\_subroutine\_smoke\_fail}
\end{center}

Failure category:

\begin{center}
\texttt{callback\_invocation}
\end{center}

Component classifications:

\begin{itemize}
  \item \texttt{hpc\_abaqus\_license\_checkout\_pass}
  \item \texttt{hpc\_user\_subroutine\_compilation\_pass}
  \item \texttt{hpc\_user\_subroutine\_link\_pass}
  \item \texttt{hpc\_standard\_analysis\_pass}
  \item \texttt{hpc\_odb\_creation\_pass}
  \item \texttt{hpc\_uexternaldb\_callback\_unverified}
  \item \texttt{hpc\_user\_subroutine\_smoke\_fail}
\end{itemize}

This is not a compiler failure, linker failure, Abaqus/Standard license failure, Standard solver-completion failure, or ODB-creation failure. It is a callback-evidence failure in the trivial smoke test. It does not run or validate the Molnar UEL/UMAT, phase-field formulation, Gate A3 benchmark reproduction, MISESERI, remeshing, or state transfer.

\section{Callback Evidence Investigation After Job 1374532.mmaster02}

\begin{tabularx}{\linewidth}{@{}lX@{}}
\toprule
Field & Value \\
\midrule
Date & 2026-07-15 \\
Investigation type & No-submit, no-Abaqus-launch, read-only evidence review \\
Diagnostic script & \path{scripts/hpc/inspect_uexternaldb_smoke_1374532.sh} \\
Investigation evidence & \path{runs/hpc/20260715_abaqus_user_subroutine_smoke_callback_investigation/} \\
Report & \path{runs/hpc/20260715_abaqus_user_subroutine_smoke_callback_investigation/CALLBACK_INVESTIGATION.md} \\
Finding & \texttt{E. insufficient\_retained\_evidence} \\
Current classification & \texttt{hpc\_uexternaldb\_callback\_unverified}; \texttt{hpc\_user\_subroutine\_smoke\_fail} \\
\bottomrule
\end{tabularx}

\subsection*{Search Locations}

The diagnostic script verified and inspected these accessible locations:

\begin{itemize}
  \item work directory: \path{/scratch/pr21vyci/adaptive-remeshing/runs/abaqus_user_subroutine_smoke_1374532.mmaster02}
  \item Abaqus scratch directory: \path{/scratch/pr21vyci/adaptive-remeshing/runs/abaqus_user_subroutine_smoke_1374532.mmaster02/abaqus_scratch}
  \item stage directory: \path{/scratch/pr21vyci/adaptive-remeshing/stage/abaqus_user_subroutine_smoke_1374532.mmaster02}
  \item repository evidence directory: \path{runs/hpc/20260715_abaqus_user_subroutine_smoke}
  \item PBS submission/repository root: \path{/home/pr21vyci/projects/adaptive-remeshing}
\end{itemize}

All required directories existed at investigation time. The original solver outputs were not edited, moved, removed, or regenerated.

\subsection*{Diagnostic Commands}

The investigation used read-only commands equivalent to:

\begin{verbatim}
find <root> -type f -printf '%p\t%s\t%TY-%Tm-%Td %TH:%TM:%TS\n'

find <root> -type f \
  \( -name 'uexternaldb_smoke.called' \
     -o -iname '*uexternaldb*' \
     -o -iname '*.so' \
     -o -iname '*.o' \
     -o -iname '*.obj' \)

grep -RInE \
  'UEXTERNALDB_SMOKE_CALLED|UEXTERNALDB|uexternaldb_smoke' \
  <root>

grep -RInEi \
  'UEXTERNALDB|compile|link|ifx|ifort|fortran|license|checked out|library|load|callback|warning|error|completed successfully|COMPLETED|ANALYSIS COMPLETE' \
  <selected text outputs>
\end{verbatim}

It was also prepared to run \texttt{file}, \texttt{nm -a}, \texttt{readelf -Ws}, and \texttt{strings} on retained shared libraries, object files, or object modules, but no retained \texttt{.so}, \texttt{.o}, or \texttt{.obj} files were found.

\subsection*{Marker Results}

The marker filename \texttt{uexternaldb\_smoke.called} was not found in the work directory, Abaqus scratch directory, stage directory, repository evidence directory, PBS submission root, or any other accessible inspected location. The marker text \texttt{UEXTERNALDB\_SMOKE\_CALLED} was found only in source/diagnostic files, not in a produced marker file.

Therefore:

\begin{itemize}
  \item marker found in run directory: no;
  \item marker found under Abaqus scratch: no;
  \item marker found in stage directory: no;
  \item marker found elsewhere accessible: no;
  \item marker write location: unknown.
\end{itemize}

\subsection*{Symbol and Library-Loading Results}

The retained evidence confirms that Abaqus accepted \texttt{user='uexternaldb\_smoke.for'}, compiled the user subroutine, and linked the user subroutine. However, the generated linked library path and generated object or shared-library files were not retained in the inspected roots. Consequently:

\begin{itemize}
  \item source compiled: yes;
  \item Abaqus linking: yes;
  \item linked \texttt{UEXTERNALDB} symbol presence: to be checked;
  \item marker strings embedded in linked library: to be checked;
  \item Abaqus user-library loading: to be checked;
  \item callback entered: unverified;
  \item marker file written: no evidence.
\end{itemize}

This evidence set does not support \texttt{callback\_not\_linked\_or\_not\_loaded}, because linking passed and no retained library is available to disprove loading. It also does not support \texttt{callback\_invocation\_confirmed\_marker\_write\_failed}, because callback entry was not directly demonstrated.

\subsection*{Analysis-Completion Evidence}

The retained \texttt{.sta} file contains \texttt{THE ANALYSIS HAS COMPLETED SUCCESSFULLY}. The retained \texttt{.msg} file reports zero warning messages during user input processing, zero warning messages during analysis, and zero error messages. The PBS output records license checkout, compilation, linking, analysis completion, and ODB creation before the script stopped at the marker check.

\subsection*{Root-Cause Status}

The precise post-investigation technical status is:

\begin{itemize}
  \item compiler environment: passed;
  \item Abaqus linking: passed;
  \item Abaqus analysis: passed;
  \item callback symbol presence: to be checked;
  \item callback library loading: to be checked;
  \item callback entry: unverified;
  \item marker write location: unknown.
\end{itemize}

Supported finding:

\begin{center}
\texttt{E. insufficient\_retained\_evidence}
\end{center}

\subsection*{Recommended Repair To Evaluate}

Do not change the Fortran source or PBS script until this evidence review is accepted. A future one-CPU retry should strengthen callback-entry evidence by evaluating one or more of the following changes:

\begin{itemize}
  \item write a unique callback token to an Abaqus-managed text stream, such as the message or data output stream, if safe from \texttt{UEXTERNALDB};
  \item write the marker using an explicit absolute path supplied by the PBS script rather than relying on the process working directory;
  \item preserve generated user-library or object artifacts, if Abaqus leaves them accessible, so \texttt{nm}, \texttt{readelf}, and \texttt{strings} can verify the linked symbol and embedded marker strings;
  \item capture exact compiler and linker command lines or generated command files when Abaqus exposes them.
\end{itemize}

Another one-CPU retry is necessary only if direct proof of \texttt{UEXTERNALDB} callback entry is required. That retry remains outside this investigation and must not run Molnar, MISESERI, remeshing, state transfer, a parameter study, or multi-CPU execution.

\section{Deterministic Callback Retry Prepared}

\begin{tabularx}{\linewidth}{@{}lX@{}}
\toprule
Field & Value \\
\midrule
Date & 2026-07-15 \\
Status & \texttt{prepared\_not\_submitted} \\
Preserved failed source & \path{tests/hpc/abaqus_standard_user_subroutine_smoke/uexternaldb_smoke.for} \\
Preserved failed PBS script & \path{scripts/hpc/abaqus_user_subroutine_smoke.pbs} \\
Retry source & \path{tests/hpc/abaqus_standard_user_subroutine_smoke/uexternaldb_smoke_getoutdir.for} \\
Retry PBS script & \path{scripts/hpc/abaqus_user_subroutine_smoke_retry.pbs} \\
Scope & One CPU, \texttt{testq}, \SI{8}{GB}, 00:30:00, trivial Abaqus/Standard smoke only \\
\bottomrule
\end{tabularx}

\subsection*{Repair Rationale}

The failed implementation for job \texttt{1374532.mmaster02} used a relative marker filename, \texttt{uexternaldb\_smoke.called}, and Fortran unit 99. The subsequent investigation found no marker file and no retained binary evidence, so callback entry, linked-symbol presence, and explicit user-library loading remained unverified.

The prepared retry does not replace the failed implementation. It adds a separate fixed-form Fortran source and a separate PBS script so the failed attempt remains reproducible.

\subsection*{Dual Callback Evidence}

The retry introduces two independent callback proofs:

\begin{itemize}
  \item an Abaqus-managed \texttt{.msg} token written through unit 7:
    \texttt{UEXTERNALDB\_CALLBACK\_ENTERED},
    \texttt{UEXTERNALDB\_MARKER\_WRITTEN}, and
    \texttt{UEXTERNALDB\_ANALYSIS\_END};
  \item an absolute marker path built with \texttt{GETOUTDIR} and written through unit 101, containing \texttt{UEXTERNALDB\_SMOKE\_CALLED}.
\end{itemize}

The source records \texttt{IOSTAT} for marker opening and prints \texttt{UEXTERNALDB\_MARKER\_OPEN\_FAILED} to the \texttt{.msg} stream if the marker cannot be opened. It also emits an end-of-analysis callback token for \texttt{LOP=3}.

\subsection*{Failure-Safe Evidence Preservation}

The retry PBS script captures the Abaqus return code with \texttt{set +e} around the Abaqus command, then restores \texttt{set -e}. It stages diagnostic evidence before enforcing acceptance checks. The staged evidence includes:

\begin{itemize}
  \item repository revision supplied through \texttt{PROJECT\_REVISION};
  \item PBS job ID;
  \item Abaqus return code;
  \item work-directory and Abaqus-scratch inventories;
  \item input and source files;
  \item available \texttt{.com}, \texttt{.log}, \texttt{.msg}, \texttt{.dat}, \texttt{.sta}, \texttt{.prt}, \texttt{.env}, and other lightweight diagnostics;
  \item callback-token search results;
  \item compiler/link/library search results;
  \item candidate object/shared-library searches and symbol/string checks where retained artifacts exist.
\end{itemize}

The ODB is not copied into the stage directory; it remains only under the scratch run directory.

\subsection*{Planned Acceptance Criteria}

The future retry may be classified as \texttt{hpc\_user\_subroutine\_smoke\_pass} only when all of the following checks pass:

\begin{itemize}
  \item Abaqus command return code is zero;
  \item retry ODB exists;
  \item retry \texttt{.sta} exists;
  \item retry \texttt{.msg} exists;
  \item marker file exists and is non-empty;
  \item \texttt{.sta} contains \texttt{THE ANALYSIS HAS COMPLETED SUCCESSFULLY};
  \item \texttt{.msg} contains \texttt{UEXTERNALDB\_CALLBACK\_ENTERED};
  \item \texttt{.msg} contains \texttt{UEXTERNALDB\_MARKER\_WRITTEN};
  \item \texttt{.msg} contains \texttt{UEXTERNALDB\_ANALYSIS\_END};
  \item marker contains \texttt{UEXTERNALDB\_SMOKE\_CALLED}.
\end{itemize}

Otherwise the retry must remain \texttt{hpc\_user\_subroutine\_smoke\_fail} with the first failed acceptance check used to refine the failure category.

\subsection*{Boundary}

This preparation was submitted only after explicit approval as one single one-CPU retry. The failed source and PBS script remain preserved separately from the retry source and PBS script.

\section{Job 1374533.mmaster02: Deterministic Callback Retry}

\begin{tabularx}{\linewidth}{@{}lX@{}}
\toprule
Item & Value \\
\midrule
Date & 2026-07-15 \\
Purpose & Verify direct \texttt{UEXTERNALDB} callback entry and marker writing after job \texttt{1374532.mmaster02} left callback invocation unverified. \\
Repository revision & \texttt{c5db808b4c8d9e9bd01a9e5da0bd91b173787b8e} \\
Queue and resources & \texttt{testq}; one node; one CPU; \SI{8}{GB}; 00:30:00 wall time \\
Compute host & \texttt{mnode097.cluster} \\
Scheduler metadata & \texttt{Resource\_List.ngpus = 1} appeared as scheduler metadata; the script did not request or use a GPU and called Abaqus with \texttt{cpus=1}. \\
Work directory & \path{/scratch/pr21vyci/adaptive-remeshing/runs/abaqus_user_subroutine_smoke_retry_1374533.mmaster02} \\
Text stage directory & \path{/scratch/pr21vyci/adaptive-remeshing/stage/abaqus_user_subroutine_smoke_retry_1374533.mmaster02} \\
PBS result & \texttt{job\_state = F}; \texttt{Exit\_status = 0} \\
PBS output & \path{/home/pr21vyci/projects/adaptive-remeshing/abq_usrsub_retry.o1374533} \\
\bottomrule
\end{tabularx}

\subsection*{Result}

The retry checked out an Abaqus/Standard license, compiled \texttt{uexternaldb\_smoke\_getoutdir.for}, linked \texttt{libstandardU.so}, completed the trivial Abaqus/Standard analysis, and returned Abaqus code zero. The work directory contains \texttt{abaqus\_user\_subroutine\_smoke\_retry.odb}, \texttt{.sta}, and \texttt{.msg}. The \texttt{.sta} file contains \texttt{THE ANALYSIS HAS COMPLETED SUCCESSFULLY}.

The callback evidence is direct and redundant. The \texttt{.msg} file contains \texttt{UEXTERNALDB\_CALLBACK\_ENTERED}, \texttt{UEXTERNALDB\_MARKER\_WRITTEN}, and \texttt{UEXTERNALDB\_ANALYSIS\_END}. The absolute marker file \path{/scratch/pr21vyci/adaptive-remeshing/runs/abaqus_user_subroutine_smoke_retry_1374533.mmaster02/uexternaldb_smoke.called} exists, is non-empty, and contains \texttt{UEXTERNALDB\_SMOKE\_CALLED}, \texttt{LOP=0}, \texttt{KSTEP=0}, and \texttt{KINC=0}. The retry script's own \texttt{acceptance\_checks.txt} lists all ten checks as \texttt{PASS}, and \texttt{final\_classification.txt} records \texttt{hpc\_user\_subroutine\_smoke\_pass}.

\subsection*{Classification}

\begin{center}
\texttt{hpc\_user\_subroutine\_smoke\_pass}
\end{center}

This pass closes the trivial HPC technical smoke sequence: PBS execution, validated module order, compiler visibility, Abaqus/Standard license checkout, user-subroutine compilation, linking, trivial Standard analysis completion, ODB creation, and direct \texttt{UEXTERNALDB} callback evidence are all passed. It does not run or validate Molnar, Gate A3, the phase-field formulation, MISESERI, remeshing, state transfer, multi-CPU execution, production execution, or any parameter study.

\section{Post-Smoke Scientific Routing Update}

The successful retry closes the HPC technical toolchain gate, but it does not change the Stage A scientific gate. Gate A3 remains \texttt{reference\_data\_insufficient}.

The active scientific route is no longer to ask the supervisor to choose whether the smaller supplementary Molnar deck should be compared exactly against Fig.~7. The thesis proposal directs the benchmark sequence: reproduce the established phase-field implementation, reproduce the unrefined Molnar benchmark, establish a uniformly fine reference, implement the Pandey--Kumar MISESERI workflow, and compare refined results against the uniform reference.

Therefore the smaller supplementary deck remains preserved unchanged as supporting technical reproducibility evidence. The next Gate A3 action is to prepare a new paper-matched Molnar Mode-I single-notch deck using the unchanged Molnar user subroutine, then digitize/document the applicable published Molnar curve as an approximate paper reference for that reconstructed configuration. No new Abaqus or PBS run is approved by this routing update.

\section{No-Run Paper-To-Model Reconstruction Audit}

Date: 2026-07-15.

This was a source-audit and benchmark-specification activity only. No Abaqus command was run, no PBS job was submitted, no preserved Molnar source or supplementary input deck was modified, and no MISESERI, remeshing, state-transfer, parameter-study, production, multi-CPU, or benchmark execution work was started.

\begin{tabular}{ll}
\toprule
Audit package & \path{references/derived/molnar_gravouil_2017/paper_matched_single_notch/} \\
Configuration skeleton & \path{configs/molnar_paper_matched_single_notch.yaml} \\
Deck requirements & \path{docs/methods/MOLNAR_PAPER_MATCHED_DECK_REQUIREMENTS.md} \\
Configuration status & \texttt{reconstruction\_audit\_incomplete}; \texttt{runnable: false} \\
Gate A3 & \texttt{reference\_data\_insufficient} \\
\bottomrule
\end{tabular}

\subsection*{Files Inspected}

\begin{itemize}
  \item \path{.agent.md}
  \item \path{THESIS_PLAN.md}
  \item \path{Literature review/1-s2.0-S0168874X16304954-main.pdf}
  \item \path{models/baseline_original/molnar_gravouil_2017/02_Single_Notch_Tension/SingleNotch.inp}
  \item \path{models/baseline_original/molnar_gravouil_2017/02_Single_Notch_Tension/SingleNotch.for}
  \item \path{references/derived/molnar_gravouil_2017/single_notch/REFERENCE_APPLICABILITY_MATRIX.md}
  \item \path{references/derived/molnar_gravouil_2017/single_notch/REFERENCE_PROVENANCE.md}
\end{itemize}

\subsection*{Parameters Confirmed}

Molnar Fig.~6 and Section~3.2 confirm the 1 mm by 1 mm single-edge-notched specimen, 0.5 mm left-edge notch, pure-tension case \(\alpha=90^\circ\), bottom fixed/top moved boundary description, plane-strain 2D setting, thickness 1 mm, \(E=210\ \mathrm{kN/mm^2}\), \(\nu=0.3\), \(G_c=2.7\times10^{-3}\ \mathrm{kN/mm}\), first paper-text length scale \(l_c=0.0075\ \mathrm{mm}\), about 22,000 elements, local crack-path mesh size \(h=0.001\ \mathrm{mm}\), and tensile increments \(\Delta u=10^{-4}\ \mathrm{mm}\) for 500 steps followed by \(\Delta u=10^{-5}\ \mathrm{mm}\). Fig.~7 visibly contains Molnar curves for \(l_c=0.015\), \(0.0075\), and \(0.005\ \mathrm{mm}\), plus Miehe symbol series.

The supplementary deck/source confirm the three-layer implementation pattern, U1 phase layer, U2 displacement layer, CPS4 \texttt{umatelem} visualization layer, \texttt{N\_ELEM=3930} for the smaller deck, RP RF/U output, and SDV output on the visualization layer.

\subsection*{Parameters Unresolved}

The audit keeps the following as unresolved rather than inventing defaults: exact mesh topology, refined-zone width/height, global element size, mesh-transition law, exact physical element count, final displacement, number of fine increments after the first 500 steps, exact digitized Fig.~7 coordinate file, matched contour-comparison displacement states, and supervisor-approved tolerances.

\subsection*{Assumptions Rejected}

\begin{itemize}
  \item The smaller supplementary \texttt{SingleNotch} deck is not treated as the exact Fig.~7 numerical model.
  \item A visually similar mesh is not accepted as a source-traceable paper-matched deck.
  \item The Fig.~7 curve is not treated as exact RF--U coordinates until digitized and assigned uncertainty metadata.
  \item The configuration is not marked runnable while critical fields remain null.
\end{itemize}

\subsection*{Reason No Abaqus Job Was Submitted}

This activity did not produce a runnable deck. It produced a non-runnable reconstruction specification and exposed critical unresolved inputs. The next controlled actions are to resolve those inputs, digitize the applicable Fig.~7 curve, prepare a versioned paper-matched deck, pass static deck checks, and only then request explicit approval for one serial HPC run.

\section{No-Run Candidate v1 Reconstruction and Static Validation}

Date: 2026-07-16.

This activity digitized the selected Fig.~7 curve, prepared candidate v1 reconstruction inputs, generated a deterministic candidate deck skeleton, and ran static checks. No Abaqus command was run, no PBS job was submitted, and the preserved Molnar supplementary files were not modified.

\begin{tabular}{ll}
\toprule
Digitized curve & Molnar Fig.~7 red dashed \(l_c=0.0075\ \mathrm{mm}\) \\
Raw digitized points & 877 \\
Processed digitized points & 91 \\
Digitization classification & \texttt{approximate\_published\_reference} \\
Estimated uncertainty & \(\pm 4\times10^{-5}\ \mathrm{mm}\), \(\pm 0.015\ \mathrm{kN}\) \\
Candidate final displacement & \(0.0067\ \mathrm{mm}\), measured from Fig.~7 extent \\
Increment schedule & 500 coarse increments plus 170 derived fine increments \\
Estimated/generated physical elements & 21,760 \\
Generated layered elements & 65,280 \\
Static validation classification & \texttt{reconstruction\_inputs\_incomplete} \\
Configuration runnable flag & \texttt{false} \\
\bottomrule
\end{tabular}

\subsection*{Assumptions Adopted}

\begin{itemize}
  \item Final displacement \(0.0067\ \mathrm{mm}\) is measured from Fig.~7 and is not explicitly stated in the paper text.
  \item Fine-step count 170 is derived from \((0.0067-0.005)/10^{-5}\).
  \item Refined-zone bounds, global size, transition width, and neighbouring-size ratio are reconstruction choices, not published parameters.
  \item Fig.~6b has no numerical displacement label; contour comparisons are therefore response-based: final converged state, peak force, and first post-peak frame at or below 50\% peak force.
\end{itemize}

\subsection*{Rejected Alternatives}

\begin{itemize}
  \item The generated mesh was not tuned solely to obtain exactly 22,000 elements.
  \item The digitized Fig.~7 curve was not promoted to exact author data.
  \item The generated deck was not marked runnable because the adopted mesh recipe still needs provenance review.
\end{itemize}

\subsection*{Generator and Validator Results}

The generator wrote \path{models/generated/molnar_gravouil_2017/paper_matched_single_notch_v1/paper_matched_single_notch_v1.inp}, \path{generation_manifest.json}, \path{parameter_snapshot.yaml}, \path{mesh_statistics.csv}, \path{source_hashes.txt}, and \path{README.md}. The initial static validation wrote \path{results/validation/molnar_paper_matched_single_notch_v1/STATIC_VALIDATION.md} with classification \texttt{reconstruction\_inputs\_incomplete}; the later provenance review supersedes this with \texttt{static\_validation\_fail}. This is a controlled stop, not a technical pass.

\section{No-Run Candidate v1 Provenance Review}

Date: 2026-07-16.

This was a no-run provenance and generated-deck review. It compared \path{configs/molnar_paper_matched_single_notch.yaml}, \path{models/generated/molnar_gravouil_2017/paper_matched_single_notch_v1/parameter_snapshot.yaml}, \path{generation_manifest.json}, \path{mesh_statistics.csv}, the Fig.~7 digitization files, source hashes, and \path{paper_matched_single_notch_v1.inp}. No Abaqus command was run and no PBS job was submitted.

The review found no mismatch in the digitized Fig.~7 point counts, manifest deck hash, generated physical/layered counts, node/element uniqueness, connectivity references, RF output set, SDV request, or absence of local Windows/HPC paths. Preserved Molnar supplementary source hashes still matched the recorded originals.

The review found static blockers:
\begin{itemize}
  \item the generated deck does not explicitly represent the left-edge notch;
  \item the generated deck lacks \texttt{*Uel property} blocks for U1/U2;
  \item the generated deck lacks an in-plane rigid-body constraint equivalent to the supplementary \texttt{bottoml}/\texttt{topl} convention;
  \item the configured coarse schedule is internally inconsistent, because \(500\times10^{-4}\ \mathrm{mm}=0.05\ \mathrm{mm}\) while the candidate coarse displacement is \(0.005\ \mathrm{mm}\);
  \item the actual Step~1 deck representation gives \(0.005/500=10^{-5}\ \mathrm{mm}\) increments, not \(10^{-4}\ \mathrm{mm}\).
\end{itemize}

No corrections were made to the generated deck during the review. The classification decision is \texttt{static\_validation\_fail}; \texttt{runnable} remains \texttt{false}. Rejected assumptions: do not treat a rectangular full plate as a notched specimen; do not infer UEL properties from YAML alone; do not accept the loading schedule from YAML without matching deck amplitudes and increments.

\section{No-Run Candidate v2 Repair and Static Validation}

Date: 2026-07-16.

Candidate v1 was preserved as failed evidence. A new versioned candidate, \texttt{paper\_matched\_candidate\_v2}, was generated under \path{models/generated/molnar_gravouil_2017/paper_matched_single_notch_v2/}. No preserved Molnar source deck or supplementary source file was modified. No Abaqus command was run and no PBS job was submitted.

The v2 repair addressed the v1 root causes as follows:
\begin{itemize}
  \item loading schedule: rejected the \(10^{-4}\ \mathrm{mm}\) Step~1 interpretation and used \(500\times10^{-5}\ \mathrm{mm}=0.005\ \mathrm{mm}\), then \(170\times10^{-5}\ \mathrm{mm}=0.0017\ \mathrm{mm}\);
  \item notch: generated split duplicated nodes on the open left-edge notch faces and validated zero elements bridging the open notch;
  \item UEL properties: restored U1 \((l_c,G_c,t)\) and U2 \((E,\nu,t,k)\) property blocks using the preserved supplementary implementation order;
  \item constraints: restored \texttt{bottoml} and \texttt{topl} in-plane constraints while retaining top-RP coupling and bottom vertical support;
  \item mesh: replaced the uniform skeleton with generated graded coordinates and diagnostics for spacings, transition ratios, aspect ratio, refined/transition/coarse element counts, and notch-adjacent elements.
\end{itemize}

The generated v2 deck hash is \texttt{f4d135d6c12d42a94c1874a6453a8865b4806a4e2d3b5018141471ba9245ecf2}; two isolated generator runs reproduced the same LF-stable hash. Static validation wrote \path{results/validation/molnar_paper_matched_single_notch_v2/STATIC_VALIDATION.md} and \path{results/validation/molnar_paper_matched_single_notch_v2/VALIDATION_RESULTS.json}. The resulting classification is \texttt{static\_validation\_pass} and the configuration has \texttt{runnable: true}.

The generated executable source pairing was repaired before submission preparation: \path{SingleNotch_v2.for} is copied from the preserved Molnar source with only \texttt{N\_ELEM} updated to \(33{,}852\), matching the candidate-v2 physical-element count. The preserved Molnar source remains unchanged.

\section{Candidate v2 Mesh-Quality Preflight and Submission Preparation}

Date: 2026-07-16.

The final mesh-quality preflight is stored at \path{results/validation/molnar_paper_matched_single_notch_v2/MESH_QUALITY_PREFLIGHT.md}. It locates all elements with aspect ratio greater than 5, 10, and 20. The maximum aspect-ratio element is 9610, with aspect ratio \(25.000000000001368\), bounds \(x=0.281..0.282\), \(y=-0.0792578132..-0.0542578132\), and positive signed area \(2.5\times10^{-5}\). The high-aspect-ratio elements do not lie in the refined fracture strip, do not intersect the expected horizontal crack path, are not at the notch tip, and do not bridge the open notch. The maximum neighbouring-size ratio remains \(1.5\). The preflight classification is \texttt{mesh\_quality\_preflight\_pass}.

The serial PBS script \path{scripts/hpc/molnar_paper_matched_single_notch_v2.pbs} was prepared for one node, one CPU, 32 GB memory, 24 hours wall time, queue \texttt{entry\_imfdfkmq}, modules \texttt{gcc/11.4.0}, \texttt{intel/2024.2.0}, and \texttt{abaqus/2023}. It stages the exact committed deck and generated candidate source to scratch, verifies their SHA-256 hashes before Abaqus execution, runs Abaqus/Standard with \texttt{cpus=1}, keeps the ODB in scratch, and stages lightweight text evidence. The run manifest is \path{runs/hpc/paper_matched_single_notch_v2/RUN_MANIFEST.md}; its initial status is \texttt{prepared\_not\_submitted}.

The run remains unexecuted because commit/push synchronization, local/HPC revision matching, clean HPC working-tree checks, and active-job checks have not yet been completed. The user's standing authorization covers exactly one future serial HPC execution after those checks pass; it does not cover retries, a second candidate, multi-CPU execution, mesh or parameter studies, MISESERI, remeshing, or state transfer.

\section{Current Stage A Boundary After These Jobs}

\begin{itemize}
  \item HPC PBS execution: passed.
  \item HPC GCC/Intel environment: passed.
  \item HPC Abaqus executable visibility: passed.
  \item HPC repository revision capture: passed.
  \item HPC Abaqus/Standard license checkout: passed for the trivial smoke.
  \item HPC trivial user-subroutine compilation: passed.
  \item HPC trivial user-subroutine linking: passed.
  \item HPC trivial Standard analysis and ODB creation: passed.
  \item HPC \texttt{UEXTERNALDB} callback invocation: passed in job \texttt{1374533.mmaster02}.
  \item Callback evidence investigation: \texttt{insufficient\_retained\_evidence}.
  \item Overall trivial user-subroutine smoke: \texttt{hpc\_user\_subroutine\_smoke\_pass}.
  \item Deterministic callback retry: completed and passed.
  \item Gate A3: \texttt{reference\_data\_insufficient}.
  \item Smaller supplementary Molnar deck: supporting technical reproducibility evidence, not the exact Fig.~7 comparison target.
  \item Next scientific benchmark target: paper-matched Molnar Mode-I single-notch deck and documented approximate paper reference.
  \item MISESERI/remeshing: blocked.
\end{itemize}

\section{Paper-Matched Candidate v2 Completed HPC Run and Postprocessing}

Date: 2026-07-16.

The single authorized serial paper-matched candidate-v2 HPC baseline completed as job \texttt{1374864.mmaster02}. No retry, second candidate, multi-CPU run, sweep, MISESERI run, remeshing run, state-transfer run, or parameter study was submitted.

\begin{table}[htbp]
\centering
\caption{Candidate-v2 completed PBS and Abaqus technical result.}
\begin{tabular}{@{}ll@{}}
\toprule
Item & Value \\
\midrule
Job ID & \texttt{1374864.mmaster02} \\
Candidate revision & \texttt{711dd495bdcb830d695f9d7e56283316c9d417d5} \\
PBS state & \texttt{F} \\
PBS exit status & \texttt{0} \\
Execution host & \texttt{mnode099/0} \\
Run count & \texttt{1} \\
Walltime & \texttt{00:38:38} \\
CPU time & \texttt{00:35:52} \\
Memory & \texttt{2970760kb} \\
VMEM & \texttt{3565868kb} \\
Abaqus return code & \texttt{0} \\
Technical classification & \texttt{paper\_matched\_v2\_technical\_pass} \\
\bottomrule
\end{tabular}
\end{table}

The technical acceptance checks passed: PBS finished with \texttt{Exit\_status = 0}, Abaqus returned zero, \texttt{.odb}, \texttt{.sta}, \texttt{.msg}, and \texttt{.dat} files exist in the scratch run directory, the \texttt{.sta} file reports \texttt{THE ANALYSIS HAS COMPLETED SUCCESSFULLY}, and the retained technical summary records \texttt{classification=paper\_matched\_v2\_technical\_pass}. The large ODB remains on scratch:

\begin{verbatim}
/scratch/pr21vyci/adaptive-remeshing/runs/molnar_paper_matched_single_notch_v2_1374864.mmaster02/molnar_paper_matched_single_notch_v2.odb
\end{verbatim}

Only lightweight evidence was copied back under \path{runs/hpc/paper_matched_single_notch_v2/}. The retained evidence includes the final scheduler record, technical summary, \texttt{.sta}, \texttt{.msg}, \texttt{.dat}, Abaqus stdout, extraction CSVs, matched-state contour CSVs, and scientific-review JSON/Markdown files.

\subsection*{Read-Only ODB Postprocessing}

The completed ODB was postprocessed read-only with Abaqus Python. The extraction generated RF--U/phase-history data, four response-based matched contour CSVs, and scientific-review diagnostics. Two scripts were made compatible with the cluster's Abaqus Python during postprocessing by removing Python-3-only file-opening keywords and replacing \texttt{math.isfinite}; these are postprocessing-tool compatibility fixes, not candidate-v2 model or solver changes.

\begin{table}[htbp]
\centering
\caption{Candidate-v2 scientific-review diagnostics.}
\begin{tabular}{@{}ll@{}}
\toprule
Metric & Value \\
\midrule
Scientific classification & \texttt{paper\_matched\_v2\_scientific\_review\_incomplete} \\
Peak RF2 & \(0.761702\ \mathrm{kN}\) at \(U_2=0.006110\ \mathrm{mm}\) \\
Final RF2 & \(0.749110\ \mathrm{kN}\) at \(U_2=0.006700\ \mathrm{mm}\) \\
RF--U NRMSE vs approximate Fig.~7 & \(0.247493\) \\
Relative peak-force error & \(0.064519\) \\
Relative peak-displacement error & \(0.041257\) \\
Final damaged elements, \(\mathrm{SDV15}\ge0.95\) & 193 \\
Final connected crack extension & about \(0.0505\ \mathrm{mm}\) \\
\texttt{SDV16} decrease count & 0 \\
\texttt{SDV15} decrease count & 6113 \\
\texttt{SDV15} events above ODB precision & 1297 \\
\texttt{SDV15} insufficient-mapping-evidence events & 817 \\
\texttt{SDV15} maximum overshoot & 1.005600 \\
\bottomrule
\end{tabular}
\end{table}

Matched-force comparisons against the approximate digitized Fig.~7 \(l_c=0.0075\ \mathrm{mm}\) curve were \(27.48\%\) high at \(U_2=0.002\ \mathrm{mm}\), \(4.98\%\) high at \(U_2=0.005\ \mathrm{mm}\), and \(11.55\%\) high at \(U_2\approx0.00599\ \mathrm{mm}\). The final \(U_2=0.0067\ \mathrm{mm}\) point lies outside the processed reference range. A no-solution forensic package was added under \path{runs/hpc/paper_matched_single_notch_v2/scientific_review/}; it records RF extraction, Fig.~7 comparison, response-state, crack-threshold, \texttt{SDV15}/\texttt{SDV16}, solver-resource audits, and the scientific decision report without modifying candidate v2 or launching a new solve.

The decision report assigns \texttt{paper\_matched\_v2\_scientific\_review\_incomplete}. The dominant RF--U mismatch is post-peak: pre-reference-peak RMSE is \(0.044136\ \mathrm{kN}\), post-reference-peak RMSE is \(0.348093\ \mathrm{kN}\), and full-overlap NRMSE is \(0.245705\). The final crack remains connected and approximately horizontal for \(\mathrm{SDV15}\) thresholds \(0.80\), \(0.90\), \(0.95\), and \(0.99\), with threshold-dependent extension from \(0.0555\ \mathrm{mm}\) down to \(0.0465\ \mathrm{mm}\). A detailed no-solution \texttt{SDV15} reconstruction under \path{runs/hpc/paper_matched_single_notch_v2/scientific_review/sdv15_detailed_review/} now preserves the raw 6113-event table, distribution, worst-event history, overshoot table, layer/update mapping, and equivalent-state categories. It reproduces all 6113 historical decreases with unique event keys, finds 1297 events above the \(10^{-6}\) ODB precision tolerance, categorizes 480 as \texttt{staggered\_sync\_effect}, and confirms 0 \texttt{SDV16} decreases at those locations. A follow-up no-solution source/deck mapping resolution under \path{runs/hpc/paper_matched_single_notch_v2/scientific_review/sdv15_mapping_resolution/} verifies all 33,852 U1/U2/CPS4 label and connectivity mappings, finds 0 mapping errors, resolves the UMAT integration-point swap, and reclassifies the remaining 817 non-staggered events as \texttt{insufficient\_output\_evidence}.

This is not a final scientific pass. The detailed \texttt{SDV15} decision is \texttt{sdv15\_detailed\_review\_incomplete}; the mapping-resolution decision is \texttt{sdv15\_mapping\_resolution\_incomplete}. Gate A3 remains \texttt{reference\_data\_insufficient} pending supervisor-approved tolerances, resolution of the remaining completed-phase-output ambiguity, and uniform-reference justification. The current authorization has been consumed by the one completed execution; retry authorization is \texttt{none}.

A supervisor-review package was prepared without running Abaqus or submitting PBS. The package consists of \path{docs/decisions/MOLNAR_GATE_A3_SUPERVISOR_REVIEW.md}, \path{docs/decisions/MOLNAR_TARGETED_OUTPUT_RERUN_REQUIREMENTS.md}, and \path{docs/handoffs/MOLNAR_GATE_A3_MEETING_SUMMARY.md}. It separates established facts, provisional working gates, unresolved scientific questions, required supervisor decisions, route consequences, and the minimum evidence that would be needed only if a targeted SDV15 output-enabled rerun is later authorized. No supervisor approval is inferred and Gate A3 remains open.

\section{Prepared Targeted SDV15 Diagnostic Run}

Date: 2026-07-16.

The user authorized exactly one serial targeted-output SDV15 diagnostic run to collect completed U1 phase-update evidence for the 817 candidate-v2 above-precision non-staggered SDV15 events. This is not a candidate-v2 retry, candidate v3, Stage B run, MISESERI run, remeshing run, state-transfer run, mesh/length/load study, or parameter sweep. If any preflight condition fails, no submission is allowed.

The diagnostic variant is \path{models/generated/molnar_gravouil_2017/paper_matched_single_notch_v2_sdv15_diagnostic/}. Candidate v2 remains unchanged in \path{models/generated/molnar_gravouil_2017/paper_matched_single_notch_v2/}. The diagnostic deck comparison records \texttt{scientific\_keyword\_equivalence\_pass}: after removing Abaqus comment lines, the diagnostic and candidate-v2 keyword/data streams match byte-for-byte. The added source logging is target-gated and writes a CSV trace under the Abaqus scratch working directory with \texttt{GETOUTDIR}; it reads computed values but does not modify numerical arrays, residuals, tangents, state updates, properties, loads, or solver controls.

\begin{table}[htbp]
\centering
\caption{Prepared SDV15 diagnostic pre-submission evidence.}
\begin{tabular}{@{}ll@{}}
\toprule
Item & Value \\
\midrule
Variant classification & \texttt{paper\_matched\_candidate\_v2\_diagnostic\_variant} \\
Initial run status & \texttt{prepared\_not\_submitted} \\
Target physical elements & 72 \\
Target element/IP pairs & 152 \\
Covered insufficient-output event rows & 817 \\
Covered staggered-sync comparison rows & 480 \\
Static validation & \texttt{diagnostic\_static\_validation\_pass} \\
Runnable flag & \texttt{diagnostic\_runnable: true} \\
PBS script & \path{scripts/hpc/molnar_paper_matched_single_notch_v2_sdv15_diagnostic.pbs} \\
Queue & \texttt{entry\_imfdfkmq} \\
Resources & \texttt{select=1:ncpus=1:mem=32gb}, \texttt{walltime=24:00:00} \\
Mail points & \texttt{\#PBS -m abe}; recipient supplied with \texttt{qsub -M} \\
\bottomrule
\end{tabular}
\end{table}

The local preflight passed the deterministic target generation, U1/U2/CPS4 layer mapping checks, source instrumentation audit, local Fortran syntax/static check with an Abaqus-parameter stub, deck scientific-keyword equivalence check, PBS bash syntax check, PBS email-notification validator, project-checklist validator, \texttt{git diff --check}, and both Stage A LaTeX compilations. The prepared postprocessor is \path{scripts/postprocessing/analyze_molnar_sdv15_targeted_diagnostic.py}; after a technical pass it will classify completed-state SDV15 behavior, verify SDV16 monotonicity, compare the diagnostic RF--U response against candidate v2, and mark the result intrusive if response changes exceed the documented non-intrusiveness limits.

The diagnostic PBS job was then submitted exactly once as \texttt{1375020.mmaster02} from repository revision \texttt{efd5f60ebb9cc6ea8ce89b508a6e9df4183e5611} at \texttt{2026-07-16T12:21:59+0200}. The scheduler accepted the mail settings \texttt{Mail\_Users = pr21vyci@mailserver.tu-freiberg.de} and \texttt{Mail\_Points = abe}. The job ran on \texttt{mnode098/0}, consumed about one second of walltime, and finished with \texttt{Exit\_status = 3}. Its PBS output contains:

\begin{verbatim}
/var/spool/pbs/mom_priv/jobs/1375020.mmaster02.SC: Zeile 40:
git: Kommando nicht gefunden.
revision_mismatch current= requested=efd5f60ebb9cc6ea8ce89b508a6e9df4183e5611
\end{verbatim}

Therefore the failure occurred before Abaqus execution at the repository-revision guard because \texttt{git} was unavailable in the batch job PATH. No ODB, \texttt{.sta}, \texttt{.msg}, or \texttt{.dat} diagnostic solver outputs were produced, and no SDV15 diagnostic scientific evidence exists from this run. The technical classification is:

\begin{center}
\texttt{molnar\_v2\_sdv15\_diagnostic\_technical\_fail}
\end{center}

Lightweight evidence is preserved under \path{runs/hpc/paper_matched_single_notch_v2_sdv15_diagnostic/evidence/1375020.mmaster02/}. Gate A3 remains \texttt{reference\_data\_insufficient}. The one-run authorization has been consumed; no retry or second diagnostic run is authorized.

\end{document}
